The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications

### 2016-02-23 DishSimulations/paper/DishSimulationsPaper_v2.tex

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
David Deboer\altaffilmark{5},
Aaron Parsons\altaffilmark{5},
Mariet Venter\altaffilmark{7}
and others.
}

@@

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014}. However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

@@

We now attempt attempt to quantify the accuracy of our time-domain simulation framework by comparing simulations to measurements of the $S_{11}$ parameter of the HERA dish. Up until now, our simulations have derived the voltage response of the dish using simulations of an incoming plane wave as is the case for radio signals arriving from objects in space. It is possible to probe the gain of the dish using objects in the far field such as known radio sources \citep{Thyagarajan:2011,Pober:2012,Colgate:2015} or constellations of ORBCOMM satellites \citep{Neben:2015,Neben:2016}. However natural radio sources are too weak to probe the dish response at the $<10^{-4}$ level necessary to verify our simulations and the ORBCOMM technique can only be used to map the gain at the single frequency that the satellites transmit at, $137$\,MHz. Work is currently underway to use broad-band transmitters flown into the far field of the dish by drones \citep{Jacobs:2016} but this system is still under development. Reflectometry of the dish using a vector network analyzer is a straightforward alternative used in \citet{Patra:2016} to estimate the gains directly. Rather than comparing their estimate of the gain with our predicted gains (which is done in this paper), we instead set up a time domain simulation to compute the $S_{11}$ parameter of HERA antenna and compare it to direct $S_{11}$ measurements.
\begin{figure}
\includegraphics[width=.5\textwidth]{figures/s11_compare.pdf}
\caption{A comparison between time-domain simulations (black lines) and measurements (grey lines) of $S_{11}$ for the HERA dish. We also show an $S_{11}$ measurement with the cables leading from the VNA to the feed terminated by an open circuit which allows us to probe the dynamic range of the measurement. We use the standard deviation of the open measurement (grey dashed line) between $100$ and $200$\,ns as our systematic floor (grey shaded region). We find very good agreement between our $S_{11}$ measurement and the simulation, validating the predictions of our simulations.}
\label{fig:S11}
\end{figure}
For

@@

\subsection{Extrapolating the Bandpass and Power Kernel}\label{ssec:Extrapolation}
Our deconvolution gives us the time-domain voltage response of the PAPER and HERA antenna elements. We plot the absolute value of this response in Fig.~\ref{fig:SimulationsCompare}, seeing that it drops to $-30$\,dB after $\approx 100$\,ns. The power-kernel that convolves visibilities to higher delays is the convolution of $\widetilde{r}(\tau)$ with its time-reversed complex conjugate, which we plot as the red line. The convolution is in very good agreement with the voltage response itself which is explained by the fact that second order terms of the convolution, approximately given by $|\widetilde{r}(\tau)|^2$ (green line) are over two orders of magnitude smaller above $50$\,ns.

Our simulations of the Dish response only extend to $\approx 300$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA at comoving scales of $\approx 0.1-0.5$\,$h$Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$, extending beyond our simulations range. To extrapolate out to higher delays, we assume that the response function is dominated by reflections between the feed and the dish. This is due to the fact that when we extend our filter bandwidth to between $50$ and $250$\,MHz and use a hamming window (which has higher resolution), we observe lobe-like structures at delays beyond $100$\,ns with a periodicity of $30$\,ns, which corresponds to the round-trip light travel time between the feed and the dish.  In addition, the long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:Simulations}), indicating that the kernel follows an exponential which we now show is indicative of reflections. We do so by adopting the notation of \citep{Patra:2016}. We let $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed. An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$. The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and so forth. The time dependent voltage at the feed from these reflections is thus
\begin{equation}
\widetilde{v}_r(t) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \widetilde{s}(t-m \tau_d)
\end{equation}
Hence
\begin{equation}
\widetilde{r}_r(\tau) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \delta_D(\tau-m\tau_d)
\end{equation}
Since the number of reflections, $m=t/\tau_d$, than we can write the long-term delay response in discrete form as 
\begin{equation}
\widetilde{r}_n \approx (\Gamma_f \Gamma_d)^{n d\tau/\tau_d}
\end{equation}
which is a power law. We thus model our discrete voltage response beyond the times sampled by our simulations as a power law
\begin{equation}
\widetilde{r} = A X^{(\tau/30\text{ns})} 
\end{equation}
We plot the best power-law fit as a dashed line inf Fig~\ref{fig:SimulationsCompare}.
%We fit our voltage response function and power-kernel to this function, finding a best fit model for the voltage kernel of $A\approx0.95$,$X \approx 0.18$, and $Y\approx 0.58$. The large $Y$ is unrepresentative of the feed reflection coefficient which has been simulated and measured to be $\approx 0.1$ for a head-on EM wave, suggesting that the reflections are arriving from the sides and potentially involve only a small component of the dish and feed. Plotting the die off for the feed reflection coefficient yields dramatically better performance than what is measured.  If the reflections are indeed originating from the sides, and a small component of the dish and feed arrangement, further suppression may be achieved through modifying this component.

@@

Given the HERA dish chromaticity, what Fourier modes will still be accessible with the delay filtering technique? To answer this question, we combine our extrapolated simulations of the HERA dish's spectral structure with simulations of foregrounds. The foreground simulations are described fully in \citep{Thyagarajan:2016} but for the readers convenience we briefly describe them here.

Our foreground model consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources sourced by radio loud AGN which combines the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz, the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz, and extrapolate point source fluxes to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}. Visibilities are computed from the diffuse and point source models assuming the achromatic HERA beam computed at $150$\,MHz and described in \citep{Neben:2016}. We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the Dish's frequency dependent gain at zenith. While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain (zenith) and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2016}.

The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities on a short time-scale cadence and performing a 1d delay CLEAN where the deconvolution is permitted to discover and subtract foregrounds within the horizon to horizon delay. Since we want to avoid CLEANing noise, the level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in terun depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step. In this work, we assume that each visibility is cleaned independently with a two minute CLEANing cadence which corresponds approximately to the time over which HERA's short baselines are coherent. The standard deviation on the real and imaginary part of a single delay transformed visibility is given by \citep{Morales:2004}
\begin{equation}
\Delta V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}}
\end{equation}
where $A_e$ is the effective area of the dish, $B$ is the bandwidth, $T_{sys}$ is the system temperature, $\tau$ is the integration time, and $k_B$ is the Boltzmann constant. The system temperature can be calculated by assuming that $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER reciever and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}. For $A_e$ we use the value of $75$\,m determined in \citep{Neben:2016}. If we assume that each baseline is cleaned independently and that the integration time is $\tau \approx 60$\,s, than the noise level at 150\,MHz is approximately $9.9$\,Jy\,MHz. In order to avoid subtracting noise, we assume that cleaning is performed down to $5\,\sigma$. In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning on a two minute cadence at the LST of 4 hours. While cleaning is able to remove structure within the horizon, it does not reduce any of the power associated with the foreground induced by the chromaticity of the dish.

To form estimates of the 21\,cm power spectrum, we split each visibility into BlackmanHarris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with an equivalent bandwidth of $10\,MHz$, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary. For each windowed interval, we use the flat sky approximation and  Fourier transform in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
\begin{equation}\label{eq:PS}
\widehat{P}({\bf k}) = \left( \frac{2 k_B}{\lambda^2} \right)^2 \frac{X^2 Y}{B_{pp} \Omega_{pp}} | \widetilde{V}({\bf u}) |^2.
\end{equation}
Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B$ is the bandwidth of the Fourier transform, and $\Omega_{pp}$ is the integrated solid angle of the primary beam squared. $X$ is a linear factor converting between $uv$ wavelengths and $k_\perp$, and $Y$ is a linear factor converting between $k_\parallel$ and the Fourier dual to frequency, $\eta$.

A drift scan instrument, HERA will be capable of observing the sky at any LST within the strip declination that passes through its primary beam. To form a final power spectrum estimate, it is expected to perform an average over the power spectrum estimates it obtains through equation~\ref{eq:PS} for each LST independently. It is well documented that foreground power is maximized over certain LST ranges \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight appropriately the LSTs in which foreground power is maximized. \citet{Thyagarajan:2016} focuses on the optimal weighting and selection of LST bins in forming a power spectrum estimate. For the purpsoes of our analysis, we focus on a single, relatively clean LST of 4 hours which includes the coldest part of the sky.

@@

Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines. We first inspect a $14.6$ and $29.2$ meter baseline in Fig.~\ref{fig:BothBaselines} and find that significant regions of the visibility are foreground free. In both baselines, we find that the residuals after cleaning tend to be at similar levels except at the subband centered at $z=8.5$ (150\,MHz), in which foreground residuals remain above the signal level out to $k_\parallel=0.23$\,$h$Mpc$^{-1}$. Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater foreground contamination as is noted in \citep{Thyagarajan:2015b}. In a real power spectrum analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.

The level of the foregrounds in Fig.~\ref{fig:BothBaselines} was derived with no attempt to apply inverse covariance weighting \citep{Parsons:2014,Ali:2015} or fringe rate filtering \citep{Parsons:2015}. In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citep{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment. Hence, as long as we can suppress our foregrounds below 1-10\,\% the signal level, they should not interfere significantly with a maximum likelihood analysis. Thus, the residuals in Fig.~\ref{fig:BothBaselines} serve as a specification for any inverse covariance weighting pipeline which will need to suppress foregrounds by between a factor of $\sim 1-10$ to bring the worst contaminated regions below the level of the signal. Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below below the level of thermal noise in most of the EoR window.

\begin{figure*}
\includegraphics[width=\textwidth]{figures/ps_compare_nithya_bothBaselines.pdf}
\caption{}
\label{fig:BothBaselines}
\end{figure*}

%\begin{figure*}
%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_7p3ew_12p6ns.pdf}
%\caption{The power spectrum computed from the delay transform of a 14.6 meter baseline in equation~\ref{eq:PS} with (solid green line) and without (solid blue line) the presence of reflections in the HERA dish. The residuals after cleaning within the dashed black lines down to three times the level of thermal noise after 20 minutes of integration with (dashed cyan) and without (red dashed) the dish chromaticity are also plotted. We find that for this short baseline, clean residuals are on a similar level as the 21\,cm signal (solid black line), indicating that a redesign of the array with fewer short baselines may be necessary to maximize its sensitivity on foreground free modes.}
%\label{fig:shortBaseline}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_1024ch_14p6ew_25p3ns.pdf}
%\caption{The same as Fig.~\ref{fig:shortBaseline} except now for a 29.2 meter baseline. We see that the level of foregrounds is down relative to our 14.6 meter baseline by two orders of magnitude, likely due to the fact that we are now outside of the region with significant contamination from the Galaxy. The presence of reflections tends to extend the $k_\parallel$ at which foregrounds drop below the level of the signal between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=0.22$\,$h$Mpc$^{-1}$ with the most severe contamination occurring at the $z=8.5$ subband where the reflections where observed to be worst in Fig.~\ref{fig:KernelsSubbands}. }
%\label{figure:shortBaseline}
%\end{figure*}

%\begin{figure*}
%\includegraphics[width=\textwidth]{figures/ps_compare_nithya_lst4hr_snrVbaselineMedian.pdf}
%\caption{The median of the ratio between foreground residuals with the chromaticity of the HERA primary beam between $k_\parallel=0.15$\,$h$Mpc$^{-1}$ and $k_\parallel=1.0$\,$h$Mpc$^{-1}$, the range of k values over which HERA will derive the majority of its sensitivity. We see that the shortest baselines tend to have relatively low signal to foreground ratios due to the presence of high amplitude Galactic synchrotron emission.}
%\label{fig:Medians}
%\end{figure*}

\subsection{The Implications of Dish Reflections on EoR Science}\label{ssec:Science}
The primary goal 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization. Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground leakage eliminates the the modes that HERA would otherwise have the greatest signal to noise detections, impacting our overall sensitivity and its ability to derive this information. In this section, we estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization. We do so using the Fisher Matrix formalism. The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer. The covariance between the parameters of some model ${\bf \theta}$ is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014,EwallWice:2015a},
\begin{equation}\label{eq:Fisher}
F_{ij} \approx \sum_{k,z} \frac{1}{\sigma^2(k,z)} \frac{\partial \Delta^2(k,z)}{\partial \theta_i} \frac{\partial \Delta^2(k,z)}{\partial \theta_j},
\end{equation}
where $\Delta^2(k,z)$ is the power spectrum amplitude for some $k-z$ bin and $\sigma^2(k,z)$ is the variance of the power spectrum estimate in that bin due to thermal noise and cosmic variance \citep{Beardsley:2013}.

>>>>

\documentclass[twocolumn]{emulateapj}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{color}
\usepackage{hyperref}
\citestyle{aa}

\begin{document}
\title{The Hydrogen Epoch of Reionization Array Dish II: Characterization of Spectral Structure with Electromagnetic Simulations and their Science Implications}
\author{
Ewall-Wice Aaron\altaffilmark{1,2},
Richard Bradley\altaffilmark{3,4},
Abraham Neben\altaffilmark{1,2},
Nipanjana Patra\altaffilmark{5},
Nithyanandan Thyagarajan \altaffilmark{6},
Jacqueline Hewitt\altaffilmark{1,2},
Zaki S. Ali\altaffilmark{5},
Judd Bowman\altaffilmark{6},
Carina Cheng\altaffilmark{5},
David Deboer\altaffilmark{5},
Aaron Parsons\altaffilmark{5},
Mariet Venter\altaffilmark{7}
and others.
}

@@

The primary obstacle to obtaining a high redshift detection of the cosmological signal through both of these methods is the existence of foregrounds that are $\sim 10^5-10^6$ times brighter. While requiring much greater sensitivity than global-signal experiments, interferometers have the advantage that spectrally smooth foregrounds are naturally contained to a finite region of Fourier space, corresponding to large line of sight scales, known as the {\it wedge} \citep{Datta:2010,Vedantham:2012,Parsons:2012,Thyagarajan:2013,Liu:2014a,Liu:2014b}. However any structure in the frequency response of the instrument is imprinted on the foregrounds and has the potential to leak power into the {\it EoR window} at small line of sight scales, masking the signal. Indeed, sub-percent spectral features in the analogue and digital signal chains on the initial build-out of the MWA are proving to be a significant obstacle \citep{Dillon:2015b,EwallWice:2015a,Beardsley:2015b}.

@@

We now attempt attempt to quantify the accuracy of our time-domain simulation framework by comparing simulations to measurements of the $S_{11}$ parameter of the HERA dish. Up until now, our simulations have derived the voltage response of the dish using simulations of an incoming plane wave as is the case for radio signals arriving from objects in space. It is possible to probe the gain of the dish using objects in the far field such as known radio sources \citep{Thyagarajan:2011,Pober:2012,Colgate:2015} or constellations of ORBCOMM satellites \citep{Neben:2015,Neben:2016}. However natural radio sources are too weak to probe the dish response at the $<10^{-4}$ level necessary to verify our simulations and the ORBCOMM technique can only be used to map the gain at the single frequency that the satellites transmit at, $137$\,MHz. Work is currently underway to use broad-band transmitters flown into the far field of the dish by drones \citep{Jacobs:2016} but this system is still under development. Reflectometry of the dish using a vector network analyzer is a straightforward alternative used in \citet{Patra:2016} to estimate the gains directly. Rather than comparing their estimate of the gain with our predicted gains (which is done in this paper), we instead set up a time domain simulation to compute the $S_{11}$ parameter of HERA antenna and compare it to direct $S_{11}$ measurements.
\begin{figure}
\includegraphics[width=.5\textwidth]{figures/s11_compare.pdf}
\caption{A comparison between time-domain simulations (black line) and measurements (grey line) of $S_{11}$ for the HERA dish. We also show an $S_{11}$ measurement with the cables leading from the VNA to the feed terminated by an open circuit which allows us to probe the dynamic range of the measurement. We use the standard deviation of the open measurement (grey dashed line) between $100$ and $200$\,ns as our systematic floor (grey shaded region). We find very good agreement between our $S_{11}$ measurement and the simulation, validating the predictions of our simulations.}
\label{fig:S11}
\end{figure}
For

@@

\subsection{Extrapolating the Bandpass and Power Kernel}\label{ssec:Extrapolation}

Our simulations of the Dish response only extend to $\approx 400$\,ns, however, we wish to understand the impact of reflections on the frequency dependent gain of an interferometer like HERA at comoving scales of $\approx 0.1-0.5$\,$h$Mpc$^{-1}$, corresponding to the delays between 180 and 900\,ns at $z=8$. To extrapolate out to higher delays, we assume that the response function is dominated by reflections between the feed and the dish. The long term falloff appears as a line on a linear-log plot (Fig.~\ref{fig:SimulationResults}), indicating that the voltage response follows an exponential which we now show is indicative of reflections. We do so by adopting the notation of \citet{Patra:2016}, letting $\Gamma_d$ represent the reflection coefficient of the Dish vertex and $\Gamma_f$ represent the reflection coefficient of the feed. An electromagnetic wave incident on the feed, at $t=0$, is accepted with amplitude $(1-\Gamma_f)$. The reflected component travels back to the dish and acquires an amplitude of $(\Gamma_f \Gamma_d)$ before returning at time, $\tau_d$ later where $(1-\Gamma_f)$ will be accepted and $\Gamma_f$ will be reflected back towards the dish. Summing the infinite series of reflections, the time dependent voltage at the feed is
\begin{equation}
\widetilde{v}_r(t) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \widetilde{s}(t-m \tau_d)
\end{equation}
implying that
\begin{equation}
\widetilde{r}_r(\tau) = \sum_m \left( \Gamma_f \Gamma_d \right)^m \delta_D(\tau-m\tau_d)
\end{equation}
Since the number of reflections is $m=t/\tau_d$, than we can write the long-term delay response in discrete form as 
\begin{equation}
\widetilde{r}_n \approx (\Gamma_f \Gamma_d)^{n d\tau/\tau_d}
\end{equation}
which is an exponential in time. We thus model our discrete voltage response beyond the times sampled by our simulations as an exponential
\begin{equation}
\widetilde{r} = A X^{(\tau/30\text{ns})} 
\end{equation}
and extrapolate the time-domain voltage response of the dish by fitting for $A$ and $X$ in our simulations between 200 and 400\,ns.

@@

Given the HERA dish chromaticity, what Fourier modes will still be accessible with the delay filtering technique? To answer this question, we combine our extrapolated simulations of the HERA dish's spectral structure with simulations of foregrounds.

The foreground model is discussed in detail in \citet{Thyagarajan:2016} but we describe them briefly here for the readers convenience. It consists of two major components: diffuse synchrotron emission from our Galaxy whose structure is described by the Global Sky Model (GSM) of \citet{deOliveiraCosta:2008} and a population of point sources sourced by radio loud AGN. The point sources include those observed in both the NRAO Sky Survey (NVSS) \citep{Condon:1998} at 1.4\,GHz and the Sydney University Mologolo Sky Survey (SUMMS) \citep{Bock:1999} at 843\,MHz. Their fluxes are extrapolated to the observed $100$-$200$\,MHz band using a spectral index of $\langle \alpha \rangle=-0.83$ determined in \citet{Mauch:2003}. Visibilities are computed from the diffuse and point source models assuming an achromatic angular response for the HERA beam computed at $150$\,MHz described in \citet{Neben:2016}. We compute two sets of visibilities: one in which the spectral structure of the dish is assumed to be completely flat, and another in which the beam is multiplied by the frequency dependent gain at zenith determined by our simulations. While this model assumes incorrectly that the frequency evolution of the primary beam is identical along all lines of sight, the majority of power enters at the beams point of maximal gain and observations of autocorrelations which reflect the angular average of the frequency dependence of all lines of sight agree well with our simulations at zenith \citep{Patra:2016}.

The foreground filtering procedure employed by PAPER and HERA involves delay transforming the visibilities and performing a 1d clean which discovers and subtract foregrounds within the horizon plus a small buffer, allowing for the suppression of foreground side-lobes in delay space. The level of foreground subtraction possible by this procedure is limited by the thermal noise level on the visibility, which in turn depends on the number of time steps and redundant baselines that are averaged before performing the cleaning step. In this work, we assume that each visibility is cleaned independently with a twenty minute cadence. Each baseline is coherent for $\approx 10$\,s per night, hence we assume that each baseline and LST is being integrated for $\approx 120$\,nights before cleaning although if we were to average over redundant baselines this number would drop enormously. The standard deviation on the real and imaginary part of a single delay transformed visibility is \citep{Morales:2004}
\begin{equation}
\sigma_V = \frac{\sqrt{2 B} k_B T_{sys}}{A_e \sqrt{\tau}},
\end{equation}
where $A_e$ is the effective area of the dish, $B$ is the bandwidth, $T_{sys}$ is the system temperature, $\tau$ is the integration time, and $k_B$ is the Boltzmann constant. For $T_{sys}$ we use the equation $T_{sys} = 100\text{K} + T_{sky}$ where $100$\,K is the temperature of the PAPER receiver and $T_{sky} = 60 (\lambda/1\,\text{meter} )^{2.55}$ is the sky temperature \citep{Fixsen:2011}. For $A_e$ we use the value of $98$\,m$^2$ determined in \citet{Neben:2016}. We assume that cleaning is performed down to five times the thermal noise level. In Fig~\ref{fig:Cleaning} we compare the delay transform of visibilities before and after cleaning at the LST of 4 hours. While cleaning is able to remove structure within the horizon, it does not reduce any of the power leaked outside of the horizon by the chromaticity of the dish.

To form estimates of the 21\,cm power spectrum, we split each visibility into Blackman-Harris windowed sub-bands centered at redshift intervals of $\Delta z = 0.5$ and each with a power equivalent bandwidth of $10$\,MHz\footnote{The end to end width of each Fourier transformed interval is 20\,MHz, however the effective width of this interval is only $\approx 0.5$ the full width since the Blackman-Harris window supresses the edge channels.}, corresponding to the redshift interval over which the statistics of the brightness temperature fluctuations are expected to be stationary. The flat sky approximation allows us to Fourier transform each interval in frequency, square, and multiply by a set of prefactors to obtain a power spectrum estimate \citep{Parsons:2014},
\begin{equation}\label{eq:PS}
\widehat{P}({\bf k}) = \left( \frac{2 k_B}{\lambda^2} \right)^2 \frac{X^2 Y}{B_{pp} \Omega_{pp}} | \widetilde{V}({\bf u}) |^2.
\end{equation}
Here, $\lambda$ is the central wavelength of the observation, $k_B$ is the Boltzmann constant, $B_{pp}$ is the integral of the square of the bandpass, and $\Omega_{pp}$ is the integral of the primary beam squared over solid angle. $X$ and $Y$ are linear factors converting between native interometry and cosmological coordinates, defined through the relation $2 \pi {\bf u}=2 \pi (u,v,\eta) = (X k_x, X k_y, Y k_z)$.

A drift scan instrument, HERA will be capable of observing the sky at any LST within the strip declination that passes through its primary beam. To form a final power spectrum estimate, it is expected to perform an average over the power spectrum estimates for each LST. It is well documented that foreground power varies significantly over LST \citep{Thyagarajan:2015a}, hence such an estimate will either filter or weight LSTS in a way that minimizes the impact of the most contaminated observations. For our analysis, we focus on a single LST of 4 hours which points out of the galactic plane and represents a relatively clean pointing similar to those we expect for HERA to concentrate its observing time on.

@@

Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for baselines of two different lengths in Fig.~\ref{fig:BothBaselines}. In both baselines, we find that the residuals after cleaning tend to be at similar levels except at the subband centered at $z=8.5$ (150\,MHz), in which foreground residuals remain above the signal level out to $k_\parallel=0.23$\,$h$Mpc$^{-1}$. Several other baselines especially those oriented entirely in the E-W direction, which we do not show, contain up to two orders of magnitude greater galactic  contamination as is noted in \citet{Thyagarajan:2015b}. In an analysis, these baselines would be down-weighted or discarded so that they do not bias our final estimate.

The level of the foregrounds in Fig.~\ref{fig:BothBaselines} is conservative since no attempt has been made to apply inverse covariance weighting techniques \citep{Tegmark:1997a,Liu:2011,Dillon:2013,Parsons:2014,Liu:2014a,Liu:2014b,Dillon:2015a,Dillon:2015b,Trott:2016} or fringe rate filtering \citep{Parsons:2015}. In order to avoid biases in a maximum likelihood analysis that determines astrophysical and cosmological parameters from our power spectra, the foregrounds should ideally be below the anticipated level of thermal noise which is shown in \citet{Pober:2014} to be on the order of a few percent the anticipated level of the cosmological signal for the full HERA deployment. Hence, as long as we can suppress our foregrounds below $\approx 1$\% the level of the signal, they should not interfere significantly with a maximum likelihood analysis. Thus, the residuals in Fig.~\ref{fig:BothBaselines} serve as a specification for any inverse covariance weighting pipeline which will need to suppress foregrounds by between a factor of $\sim 1-10$ to bring the worst contaminated regions below the level of the signal. Applications of inverse covariance filters in recent PAPER observations have yielded improvements at and above this level {\bf \color{red} citation?}, hence our simulations show that even with the presence of beam chromaticity, HERA will be able to isolate foregrounds below the level of thermal noise in most of the EoR window.

\begin{figure*}
\includegraphics[width=\textwidth]{figures/ps_compare_nithya_bothBaselines.pdf}
\vspace{-24pt}
\caption{The delay transform power spectrum for different baselines over several redshifts with (green solid line) and without (blue solid line) the presence of the simulated chromaticity in the HERA dish. Each estimate is computed using the square of a Blackman-Harris windowed  delay transform (equation~\ref{eq:PS})) over an equivalent power bandwidth of $10$\,MHz. We also show the power spectra of foreground residuals after cleaning the entire $100$\,MHz band with (dashed cyan line) and without (red dashed line) the beam spectral structure. For all subbands except $z=8.5$, we find that the reflections in the HERA dish have a negligible effect on the $k_\parallel$ where the foregrounds drop below the signal level. This is the same subband where enhanced spectral structure due to reflections are observed in our simulations (Figs.~\ref{fig:KernelsSubbands} and \ref{fig:Residuals}).}
\label{fig:BothBaselines}
\end{figure*}

\subsection{The Implications of Dish Reflections on EoR Science}\label{ssec:Science}
A primary near-term goal of 21\,cm EoR observations is to obtain information about the nature of the sources that drove reionization. Since the amplitude of the 21\,cm signal is maximal at smaller $k$ values, a loss of large scale signal due to foreground contamination eliminates the the modes that HERA would otherwise have the greatest signal to noise detections of, reducing its overall sensitivity. In this section, we use the Fisher Matrix formalism to estimate the impact of foreground leakage on HERA's sensitivity along with its ability to determine the astrophysics of reionization. The Fisher Matrix allows us to forecast the covariances and errors on reionization parameters given errors on power spectrum observations due to the uncertainties caused by cosmic variance and thermal noise which is in turn determined by the $uv$ coverage and observing time of the interferometer. The covariance between the parameters of some model ${\bf \theta}$ is given by the inverse of the Fisher matrix, ${\bf F}$ which for Gaussian and independently determined power spectrum bins may be written approximately as \citep{Pober:2014},
\begin{equation}\label{eq:Fisher}
F_{ij} \approx \sum_{k,z} \frac{1}{\sigma^2(k,z)} \frac{\partial \Delta^2(k,z)}{\partial \theta_i} \frac{\partial \Delta^2(k,z)}{\partial \theta_j},
\end{equation}
where $\Delta^2(k,z)$ is the power spectrum amplitude for some $k-z$ bin and $\sigma^2(k,z)$ is the variance of the power spectrum estimate in that bin due to thermal noise and cosmic variance \citep{Beardsley:2013}. We write this equation as approximate since it ignores terms arising from the dependence of $\sigma^2(k,z)$ on model parameters due to cosmic variance but only contribute at the $\approx 1$\% level \citep{EwallWice:2015b}.
